---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

# Multiple Sclerosis Lesion Data

The data in this repository is from the Laboratory of Imaging Technologies (http://lit.fe.uni-lj.si/tools.php?lang=eng).

## Cross-sectional data

The cross-sectional data is from the "3D MR image database of Multiple Sclerosis patients with white matter lesion segmentations" section of the website.  

The database is released under the Creative-Commons 
Attribution (CC-BY) license. Please cite the references 
below in any published work that uses this database.

![](https://mirrors.creativecommons.org/presskit/buttons/88x31/svg/by.svg)

### References 
The data is described in:
Lesjak, Žiga, et al. "A novel public MR image dataset of multiple sclerosis patients with lesion segmentations based on multi-rater consensus." Neuroinformatics (2017): 1-13.

### Raw Data

```{r, echo=FALSE, message=FALSE}
library(neurobase)
library(dplyr)
library(tidyr)
x = list.files(
  path = "cross_sectional/raw", pattern = ".nii.gz", 
  recursive = TRUE, full.names = TRUE)
mods = nii.stub(x, bn = TRUE)
mods = recode(mods, "consensus_gt" = "Gold_Standard",
       T1W = "T1", T1WKS = "T1Post", T2W = "T2")
x = paste0("[", mods, "](", x, ")")
df = data_frame(file = x, mod = mods, id = basename(dirname(x)))
df = spread(df, key = mod, value = file)
knitr::kable(df, col.names = rep("", ncol(df)))
```

## Longitudinal data

The cross-sectional data is from the "Longitudinal MR image database of Multiple Sclerosis patients with white matter lesion change segmentation" section of the website.  

This archive contains longitudinal Magnetic Resonance (MR) images of patients with Multiple Sclerosis (MS) with corresponding
ground truth segmentations of white matter lesion changes. Each patient has been imaged twice on two separate occasions. The
images are grouped intro folders for each of the patients. 

The database is released under the Creative-Commons 
Attribution (CC-BY) license. Please cite the references 
below in any published work that uses this database.

![](https://mirrors.creativecommons.org/presskit/buttons/88x31/svg/by.svg)

### Description
This archive contains longitudinal Magnetic Resonance (MR) images 
of Multiple Sclerosis (MS) patients with corresponding ground 
truth segmentations of white matter lesion changes. Each patient 
has been imaged twice on two separate occasions. The images are 
grouped into folders for each of the patients. Each patient's 
folder consists of:
- Co-registered and N4 corrected T1-weighted, T2-weighted and FLAIR images for both MR studies 
- Brain mask 
- White matter lesion change mask
- RAW images in their original space 
- Intra-study transform parameters and transform parameters from RAW to common space

### References 
The data is described in:
Lesjak, Žiga, Franjo Pernuš, Boštjan Likar, and Žiga Špiclin. "Validation of White Matter Lesion Change Detection Methods on a Novel Publicly Available MRI Image Database." Neuroinformatics (2016): 1-18.


